---
title: "COMP1014 / MATH7016 Assignment Autumn 2025"
author: "Ricky Melo, and Dylan Costa"
date: "Due 20-05-2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### ASSIGNMENT CASE
### -----------------------
### Australian Neuroplasticity and Learning Efficiency Study
Sleep quality and cognitive function play a vital role in overall well-being and
productivity. This study examines these factors in adults aged 20-35 across
Australia, including individuals from various occupational backgrounds and
lifestyles. It explores how sleep patterns, lifestyle habits, and daily routines
influence learning efficiency and cognitive adaptability.

### Data Collection Process
The study used stratified random sampling to capture participants from
diverse occupations and lifestyles. Recruitment was conducted through
university mailing lists, workplace wellness programs, and social media,
resulting in a final sample of 300 individuals selected after screening.

### Data Sources:
• Wearable device tracking: All participants used wrist-based trackers to
measure sleep duration, sleep consistency, and physical activity levels.
• Self-reported surveys: Participants completed structured questionnaires on
diet, caffeine intake, screen time, stress, and social interactions.
• Cognitive performance tests: Standardised assessments measured memory,
reaction time, and logical reasoning over three months.



### Question 2: Test whether gender is independent of nap frequency.
```{r}
SleepCogStudy <- read.csv("Resources/Sleep_Cognition_Study_f1PhaXA.csv")
```

```{r}
# Initalise Table
table(SleepCogStudy$Gender, SleepCogStudy$NapFrequency)
genderTable = matrix(c(43,41,33,38,28,27,28,47,1,1,2,4,2,1,2,2), ncol = 4)

dimnames(genderTable) = list(gender = c("Female","Male","Non-Binary", "Other"), 
                             napFrequency = c("Never", "Often","Rarely", "Sometimes"))

barplot(genderTable, col = c("pink", "skyblue", "yellow", "brown"), beside = TRUE, legend = rownames(genderTable),
        main = "Nap Frequency by Gender",
        xlab = "Nap Frequency",
        ylab = "Count")   
```


```{r}
# H0: Gender is independent of nap frequency
# HA: Gender is dependent of nap frequency

# Expected Values
gender.count = rowSums(genderTable)
napFrequency.counts = colSums(genderTable)
outer(gender.count, napFrequency.counts) / sum(genderTable)

# Test independence of gender on nap frequency
chisq.test(genderTable, simulate.p.value = TRUE)
# p-value = 0.5662 

# Conclusion:
# As the p-value is greater than 0.05
# we do not reject the null hypothesis
```



## Question 3
Test whether participants who use melatonin supplements have significantly longer average sleep durations than those who don’t.

## Question 4
Test whether average sleep duration vary significantly across different genders.

### Q5. Test if screen time before bed can be used to predict average sleep duration among office workers.
``` {r}
# Load csv file
SleepCogStudy <- read.csv("Resources/Sleep_Cognition_Study_f1PhaXA.csv")
 
#H0: Screen time before bed has no effect on average sleep duration
#HA: Screen time before bed significantly predicts average sleep duration 

#H0: m1 = 0
#hA: m1 =/= 0

#Filter data to office workers
office_data <- subset(SleepCogStudy, OccupationType == "Office Worker")

# Fit linear regression model 
fit <- lm(AverageSleepDuration ~ ScreenTimeBeforeBed, data = office_data)
summary(fit)

#plot Sleep Duration vs. Screen Time 
plot(office_data$ScreenTimeBeforeBed, office_data$AverageSleepDuration,
     main = "Sleep Duration vs. Screen Time (Office Workers)",
     xlab = "Screen Time Before Bed (hours)",
     ylab = "Average Sleep Duration (hours)",
     pch = 19, col = "darkgreen")
abline(fit, col = "red", lwd = 2)

```
Test if screen time before bed can be used to predict average sleep duration among office workers.
• Fit to a suitable model and show all key steps.
• Assess the strength of the predictive power of the model.
• Plot the residuals. What do they suggest about the model?
    

## Question 6
Which of your results surprised you and why? What would you test if you had more time and interest?

Only create a question and explain the solution method in words.

