---
title: "Question 3"
author: "Ricky and Dylan"
date: "2025-05-17"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Question 3

Test whether participants who use melatonin supplements have significantly longer average sleep durations than those who don’t.

# Hypothesis

Null Hypothesis H0 - There is not a difference between melatonin users and non melatonin users for average sleep duration.

Alternative Hypothesis H1 - Users that use melatonin have a longer average sleep duration than non melatonin users.

```{r}
SleepCogStudy <- read.csv("Resources/Sleep_Cognition_Study_f1PhaXA.csv")
```

```{r}
usesMelatonin <- SleepCogStudy[SleepCogStudy$MelatoninUse == 1, ]
noMelatonin <- SleepCogStudy[SleepCogStudy$MelatoninUse == 0, ]

mean(usesMelatonin$AverageSleepDuration)
mean(noMelatonin$AverageSleepDuration)

t.test(usesMelatonin$AverageSleepDuration, noMelatonin$AverageSleepDuration)
```

# Conclusion

As the p value is less that 0.05 we can prove the alternative hypothesis that melatonin users have a longer average sleep duration than non melatonin users.
