---
title: "Question 1"
author: "Ricky and Dylan"
date: "2025-05-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Question 1

ASSIGNMENT CASE

-----------------------

Australian Neuroplasticity and Learning Efficiency Study

Sleep quality and cognitive function play a vital role in overall well-being and productivity. This study examines these factors in adults aged 20-35 across Australia, including individuals from various occupational backgrounds and lifestyles. It explores how sleep patterns, lifestyle habits, and daily routines influence learning efficiency and cognitive adaptability.

Data Collection Process

The study used stratified random sampling to capture participants from diverse occupations and lifestyles. Recruitment was conducted through university mailing lists, workplace wellness programs, and social media, resulting in a final sample of 300 individuals selected after screening.

Data Sources:

• Wearable device tracking: All participants used wrist-based trackers to measure sleep duration, sleep consistency, and physical activity levels.

• Self-reported surveys: Participants completed structured questionnaires on diet, caffeine intake, screen time, stress, and social interactions.

• Cognitive performance tests: Standardised assessments measured memory, reaction time, and logical reasoning over three months.

The variables in the dataset are given below.

```{r}
SleepCogStudy <- read.csv("Resources/Sleep_Cognition_Study_f1PhaXA.csv")
#SleepCogStudy
```

#### - Dataset Variables (Columns):

- ParticipantID: Unique identifier for each participant.
- Age: Age of the participant.
- Gender: Gender of the participant (Male/Female/Non-binary/Other).
- OccupationType: General category of employment (Student, Office Worker, Healthcare, Tradesperson, Night-shift Worker, Unemployed, etc.).
- AverageSleepDuration: Average hours of sleep per night.
- SleepQualityIndex: Self-reported sleep quality score (1-10, where 10 is excellent).
- SleepConsistency: Standard deviation in sleep duration across nights (higher values indicate irregular sleep patterns).
- CaffeineIntake: Number of caffeinated drinks per day (0, 1, 2, 3, etc.).
- PhysicalActivityLevel: Hours of moderate-to-vigorous physical activity per week.
- ScreenTimeBeforeBed: Minutes spent on screens (phone, TV, laptop) before sleep.
- BlueLightExposure: 1 if participant frequently uses screens without blue light filters at night, 0 otherwise.
- StressLevel: Self-reported stress level on a scale from 1 (Low) to 10 (High).
- DietQualityIndex: Composite score (1-10) based on dietary quality, with 10 being the healthiest.
- CognitiveTestScore: Average performance score on cognitive tests measuring reaction time, memory recall, and logical reasoning (0-100%).
- MorningAlertness: Self-reported alertness level in the morning (1-10).
- CommuteTime: Total daily commute time (in minutes).
- Chronotype: Self-identified sleep preference (Morning Type, Evening Type, Neither).
- NapFrequency: How often the participant takes daytime naps (Never, Rarely, Sometimes, Often).
- SocialInteractionScore: Self-reported rating of daily social interaction levels (1-10).
- MelatoninUse: 1 if the participant uses melatonin supplements, 0 otherwise.
- MentalHealthHistory: 1 if the participant has been diagnosed with anxiety/depression, 0 otherwise.

Please conduct all the analyses as outlined using this dataset in the sections below.
