---
title: "Question 3"
author: "Ricky and Dylan"
date: "2025-05-17"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Question 3
Test whether participants who use melatonin supplements have significantly longer average sleep durations than those who don’t.

# Hypothesis
Null Hypothesis H0 - There is not a difference between melatonin users and non melatonin users for average sleep duration.

Alternative Hypothesis H1 - Users that use melatonin have a longer average sleep duration than non melatonin users.

```{r}
SleepCogStudy <- read.csv("Resources/Sleep_Cognition_Study_f1PhaXA.csv")
```

```{r}
usesMelatonin <- SleepCogStudy[SleepCogStudy$MelatoninUse == 1, ]
noMelatonin <- SleepCogStudy[SleepCogStudy$MelatoninUse == 0, ]

boxplot(usesMelatonin$AverageSleepDuration, noMelatonin$AverageSleepDuration,
        names = c("Melatonin Users", "Non Melatonin Users"),
        ylab = "Average Sleep Duration (hours)",
        main = "Sleep Duration based off Melatonin Use",
        col = c("blue", "red"))
```

# Expectation
Based from the boxplot, we can predict a statistically significant difference if people who use melatonin show noticeably longer sleep lengths. It then makes sense to assume that melatonin users might sleep longer based on their use of a melatonin.

```{r}
mean(usesMelatonin$AverageSleepDuration)
mean(noMelatonin$AverageSleepDuration)

t.test(usesMelatonin$AverageSleepDuration, noMelatonin$AverageSleepDuration)
```

# Conclusion
If the p value less than 0.05 we can reject the null hypothesis and then accept the alternative that melatonin users sleep longer.

If the p value is greater or equal 0.05 we fail to reject the null hypothesis.

## Interpreation
As the p value is less that 0.05 we can prove the alternative hypothesis that melatonin users have a longer average sleep duration than non melatonin users.

## Was the expectation correct?
Yes it was as the box plot showcased a difference and then hypothesis test statistically confirmed it.

# Errors or Warnings

I encountered some issues in regards to how to format t.test function but after looking at the r documentation and a youtube video I was able to correct the syntax errors I had made and get the code working.
