---
title: "Question 1"
author: "Ricky and Dylan"
date: "2025-05-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Question 1

ASSIGNMENT CASE

-----------------------

Australian Neuroplasticity and Learning Efficiency Study

Sleep quality and cognitive function play a vital role in overall well-being and productivity. This study examines these factors in adults aged 20-35 across Australia, including individuals from various occupational backgrounds and lifestyles. It explores how sleep patterns, lifestyle habits, and daily routines influence learning efficiency and cognitive adaptability.

Data Collection Process

The study used stratified random sampling to capture participants from diverse occupations and lifestyles. Recruitment was conducted through university mailing lists, workplace wellness programs, and social media, resulting in a final sample of 300 individuals selected after screening.

Data Sources:

• Wearable device tracking: All participants used wrist-based trackers to measure sleep duration, sleep consistency, and physical activity levels.

• Self-reported surveys: Participants completed structured questionnaires on diet, caffeine intake, screen time, stress, and social interactions.

• Cognitive performance tests: Standardised assessments measured memory, reaction time, and logical reasoning over three months.

```{r}
SleepCogStudy <- read.csv("Resources/Sleep_Cognition_Study_f1PhaXA.csv")
```
The variables in the dataset are given below.

